Index measures for oak decline severity using phenotypic descriptors

### 2020-03-13 manuscript/manuscript.Rmd
package cache update. Couple of small manuscript adjustments

Machine learning is finding increasing utility in ecological and environmental applications due to its ability to learn complex patterns within and between variables [@cutler2007;@belgiu2016].
A popular algorithm is random forest due to it's versatility, relatively simple model training requirements and ease of use. 
It is an ensemble machine learning method where forests of bootstrap sampled decision trees are grown, yielding both out of bag sample prediction accuracies and variable importance [@breiman2001a;@biau2016].

@@

The collected phenotypic descriptors related to tree shape, size, crown condition and the presence of biotic agents including insects, bacteria and fungi are listed and described in Supplementary Table 1.
Surveyors involved in phenotyping the trees used in this study had prior experience conducting ICP-Forests level I crown condition surveys. 
In each year of sampling surveyors met to undergo refresher training and “calibration” assessments in oak woodland. 
The descriptors collected were based on @innes1990 and @icpforests2016.
Diameter at breast height (DBH) was collected at a stem height of 1.3m, to the nearest 1mm.
Total height, timber height and lowest live crown were measured using an inclinometer to the nearest 0.1m.
The timber height was measured at either where the top stem diameter was 70mm or where no main stem could be distinguished.
For crown contact, missing crown and absolute crown transparency, percentages were visually estimated between 0 and 100% in 5% interval classes.

>>>>

Machine learning is finding increasing utility in ecological and environmental applications due to it's ability to learn complex patterns within and between variables [@cutler2007;@belgiu2016].
A popular algorithm is random forest due to it's versatility, relatively simple model training requirements and ease of use. 
It is an ensemble machine learning method where forests of bootstrap sampled decision trees are grown, yielding both 'out of bag' sample prediction accuracies and variable importance [@breiman2001a;@biau2016].

@@

The collected phenotypic descriptors related to tree size, crown condition and the presence of biotic agents including insects, bacteria and fungi are listed and described in Supplementary Table 1.
Surveyors involved in phenotyping the trees used in this study had prior experience conducting ICP-Forests level I crown condition surveys. 
In each year of sampling surveyors met to undergo refresher training and “calibration” assessments in oak woodland. 
The descriptors collected were based on @innes1990 and @icpforests2016.
Diameter at breast height (DBH) was collected at a stem height of 1.3m, to the nearest 1mm.
Total height, timber height and lowest live crown were measured using an inclinometer to the nearest 0.1m.
The timber height was measured at either where the top stem diameter was 70mm or where no main stem could be distinguished.
For crown contact, missing crown and absolute crown transparency, percentages were visually estimated between 0 and 100% in 5% interval classes.
